### 2021-02-20 experiments.tex
python loc data
clarify no bugs

For Python, we analyzed the top 25 GitHub projects by our criteria (see above), due to the smaller size of Python projects.  These ranged in size from 3,377 LOC to 34,671 LOC, with a total size of just under 100 KLOC.  We analyzed 158,418 valid mutants.

@@

For Python, all but three of the mutants we examined for {\bf RQ 5} (a random sample of 100 mutants with a kill difference) involved code changes we agreed would introduce a real bug in the code if it was executed.  The large majority involved statement deletions, detected via 1) unused variables/arguments, 2) instances lacking a member field, or 3) undefined variables.  Interestingly, this seems to be an engine issue more than a detector issue, as pyflakes and Pylint both basically support all of these kinds of checks.  In some cases the two tools both detected a problem (but PyChecker did not) but differed as to \emph{which} variable was not used or defined, again suggesting an engine rather than detection rule difference.  Pylint's better performance was mostly, in the sample, due to detecting more of these issues, though it also was the only tool in the sample that detected arithmetic operation changes, due as far as we could determine to constant index changes.  Pylint also detected a few mutants no other tool did, due to the presence of unreachable code.  In one case, it also noticed a protected member access via a change in constant index, a surprisingly complex problem to find, in our opinion.  PyChecker was never the sole detecting tool for any mutants in our sample.

>>>>

For Python, we analyzed the top 25 GitHub projects by our criteria (see above), due to the smaller size of Python projects.  These ranged in size from 137 LOC to 29,339 LOC, with a total size of about 75 KLOC, and a mean size of 3,185 LOC.  We analyzed 158,418 valid, non-TCE redundant, mutants taken from these programs.

@@

For Python, all but three of the mutants we examined for {\bf RQ 5} (a random sample of 100 mutants with a kill difference) involved code changes we agreed were definitely buggy, and would cause incorrect behavior if executed (the exceptions were deletions of code with no effect on state, e.g., strings as comments).  The large majority involved statement deletions, detected via 1) unused variables/arguments, 2) instances lacking a member field, or 3) undefined variables.  Interestingly, this seems to be an engine issue more than a detector issue, as pyflakes and Pylint both basically support all of these kinds of checks.  In some cases the two tools both detected a problem (but PyChecker did not) but differed as to \emph{which} variable was not used or defined, again suggesting an engine rather than detection rule difference.  Pylint's better performance was mostly, in the sample, due to detecting more of these issues, though it also was the only tool in the sample that detected arithmetic operation changes, due as far as we could determine to constant index changes.  Pylint also detected a few mutants no other tool did, due to the presence of unreachable code.  In one case, it also noticed a protected member access via a change in constant index, a surprisingly complex problem to find, in our opinion.  PyChecker was never the sole detecting tool for any mutants in our sample.
